SubsidyExplorer - Step 6: Run Model

### 2020-09-17 scripts/07_proposals.Rmd
static results update

```{r setup, include=FALSE}
# Load packages
library(knitr) 
library(tidyverse)

@@

Make nice looking table showing most ambitious result values (global and regional)

```{r}
# most_ambitious_results_global <- most_ambitious_results %>%
#   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
#     summarize(BAU_tot = sum(BAU, na.rm = T),
#               Reform_tot = sum(Reform, na.rm = T),
#               Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
#                             TRUE ~ 0)) %>%
#     ungroup() %>%
#     mutate(Region = "Global") %>%
#     # mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
#     #                             Variable == "catches_total" ~ "Catches",
#     #                             Variable == "revenue_total" ~ "Revenue",
#     #                             Variable )) %>%
#   dplyr::filter(Fleet == "Total") %>%
#   dplyr::filter(Variable %in% c("Biomass", "Catches", "Revenue"))
```

>>>>

```{r setup, include=FALSE}
# Load packages
library(knitr) 
library(tidyverse)
library(countrycode)

@@

## Extract 2060 and end year results for all proposals and save as nice tables

```{r}
all_results_global_output_table <- plot_results %>%
  dplyr::filter(Year %in% c(2060, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
  summarize(BAU_tot = sum(BAU, na.rm = T),
            Reform_tot = sum(Reform, na.rm = T),
            Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
                            TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches",
                                Variable == "revenue_total" ~ "Revenue",
                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Diff_tot,
                Variable) %>%
  spread(Variable, Diff_tot)

write.csv(all_results_global_output_table, paste0(results_dir, "all_results_global_output_table.csv"))

# Get rounded end values
global_biomass_2060 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2060 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
global_biomass_end <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)

global_catches_2060 <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == 2060 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)

# Now do regional
all_results_regional_output_table <- plot_results %>%
  dplyr::filter(Year %in% c(2060, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches",
                                Variable == "revenue_total" ~ "Revenue",
                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Region,
                Diff,
                Variable) %>%
  spread(Variable, Diff)

write.csv(all_results_regional_output_table, paste0(results_dir, "all_results_regional_output_table.csv"))
```

## Do the same with aboslute values

```{r}
# Weight of a mature dairy cow in mt
cow_weight <- 0.6803886

all_results_global_cow_equivalent_table <- plot_results %>%
  dplyr::filter(Year %in% c(2060, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
  summarize(BAU_tot = sum(BAU, na.rm = T),
            Reform_tot = sum(Reform, na.rm = T),
            abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
                                     TRUE ~ 0),
            cow_Diff = abs_Diff_tot*cow_weight) %>%
  ungroup() %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                              Variable == "catches_total" ~ "Catches")) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                cow_Diff,
                Variable) %>%
  spread(Variable, cow_Diff)

write.csv(all_results_global_cow_equivalent_table, paste0(results_dir, "all_results_global_cow_equivalent_table.csv"))

all_results_regional_cow_equivalent_table <- plot_results %>%
  dplyr::filter(Year %in% c(2060, end_year)) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                Variable == "catches_total" ~ "Catches")) %>%
  mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
                              TRUE ~ 0),
         cow_Diff = abs_Diff*cow_weight) %>%
  dplyr::select(Id = run_id,
                Name = run_name,
                Category = run_group, 
                Year,
                Region,
                cow_Diff,
                Variable) %>%
  spread(Variable, cow_Diff)

write.csv(all_results_regional_cow_equivalent_table, paste0(results_dir, "all_results_regional_cow_equivalent_table.csv"))
